Logarithmic Space Verifiers on NP-complete

### 2019-10-26 doc/manuscript.tex
Fixed a content doc detail
Updated content doc

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P. Another major complexity classes are L and NL. The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier. NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1. To attack the P versus NP problem, the NP-completeness is a useful concept. We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
\end{abstract}

@@

The $P$ versus $NP$ problem is a major unsolved problem in computer science \cite{CS00}. This is considered by many to be the most important open problem in the field \cite{CS00}. It is one of the seven Millennium Prize Problems selected by the Clay Mathematics Institute to carry a US\$1,000,000 prize for the first correct solution \cite{CS00}. It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency \cite{AS17}. However, the precise statement of the $P=NP$ problem was introduced in 1971 by Stephen Cook in a seminal paper \cite{CS00}. In 2012, a poll of 151 researchers showed that 126 (83\%) believed the answer to be no, 12 (9\%) believed the answer is yes, 5 (3\%) believed the question may be independent of the currently accepted axioms and therefore impossible to prove or disprove, 8 (5\%) said either do not know or do not care or don't want the answer to be yes nor the problem to be resolved \cite{GA12}. It is fully expected that $P \neq NP$ \cite{Pap03}. Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}. For that reason, $P = NP$ is considered as a very unlikely event \cite{Pap03}. Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}. Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}. In this work, we show some results that might be helpful in facing one of the most important open problems in computer science.

@@

@@

\begin{proof}
Given a valid instance $(\psi, K)$ for $MIN\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not a valid certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain that:
\[(\psi, K) \in MIN\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is a valid certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{2-algorithm}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$. In addition, we reject immediately when the following comparisons
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

@@

\begin{theorem}
The Hypothesis \ref{hypothesis} is true.
\end{theorem}

@@

@@

This work is implemented into a GitHub Project programmed in Scala \cite{FV19}. In this GitHub Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}. We need to install JDK 8 in order to test the Scala Project \cite{OD16}. In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P. Another major complexity classes are L and NL. The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier. NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1. To attack the P versus NP problem, the NP-completeness is a useful concept. We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L. In this way, there is an NP-complete language which complies with an equivalent certificate-based definition of NL, and therefore P = NP.
\end{abstract}

@@

In previous years there has been great interest in the verification or checking of computations \cite{LIP90}. Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}. Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifer is a time bounded computation \cite{LIP90}. In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}. Besides, a probabilistic logarithmic space verifiers have been shown for $NP$ such that these are based on a technique of Lipton \cite{LIP90}. In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.

\section{Motivation}

The $P$ versus $NP$ problem is a major unsolved problem in computer science \cite{CS00}. This is considered by many to be the most important open problem in the field \cite{CS00}. It is one of the seven Millennium Prize Problems selected by the Clay Mathematics Institute to carry a US\$1,000,000 prize for the first correct solution \cite{CS00}. It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency \cite{AS17}. However, the precise statement of the $P=NP$ problem was introduced in 1971 by Stephen Cook in a seminal paper \cite{CS00}. In 2012, a poll of 151 researchers showed that 126 (83\%) believed the answer to be no, 12 (9\%) believed the answer is yes, 5 (3\%) believed the question may be independent of the currently accepted axioms and therefore impossible to prove or disprove, 8 (5\%) said either do not know or do not care or don't want the answer to be yes nor the problem to be resolved \cite{GA12}. It is fully expected that $P \neq NP$ \cite{Pap03}. Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}. For that reason, $P = NP$ is considered as a very unlikely event \cite{Pap03}. Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}. Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}.

@@

\begin{theorem}
\label{argument}
If the Hypothesis \ref{hypothesis} is true, then there is an $\textit{NP--complete}$ language which complies with an equivalent certificate-based definition of $NL$, and therefore $P = NP$.
\end{theorem}

\begin{proof}
From the early days of automata and complexity  theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}. Each model is deterministic and has a read-only input tape and some infinite work tapes \cite{KU15}. The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}. In the terminology of the (generalized) Turing machine models are called two-way and one-way deterministic Turing machines respectively \cite{KU15}.

The languages accepted by one-way deterministic logarithmic space Turing machine coincide with the class $L$ \cite{KU15}. The reason is because the classes of languages accepted by restricted and strongly $f$ space-bounded one-way deterministic Turing machine coincide, for any space constructible function $f$ on deterministic Turing machines \cite{KU15}. A function $f$ is space constructible if there exists a Turing machine $M$ which, given a string $1^{n}$ consisting of $n$ ones, outputs the binary (or unary) representation of $f(n)$, while using only $O(f(n))$ space \cite{KU15}. For the restricted and strongly mode, the space is bounded by the condition that,  given a function $f$, the Turing machine uses at most $f(i)$ cells of the work tapes in any configuration with input head at position $i$, occurring in any accepting computation \cite{KU15}. In this way, a logarithmic space computable function $f$ complies with the definition above \cite{MS06}.

In this way, we can accept the elements of the language $L_{1} \in L$ by a one-way deterministic logarithmic space Turing machine $M'$ \cite{KU15}. In addition, we can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}. Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}. At the same time, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will output 1 when $w \in L_{2}$. Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which accepts the language $L_{2}$.

The reason is because we can simulate the output string of $N(w)$ within a read-once output tape and thus, we can compute in logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}. Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the one-way deterministic logarithmic space Turing machine $M'$. Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}. If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}. Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$.
\end{proof}

@@

\begin{proof}
Given a valid instance $(\psi, K)$ for $MIN\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not a valid certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain the array $A$ is also a valid certificate when:
\[(\psi, K) \in MIN\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is a valid certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{2-algorithm}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$. In addition, we reject immediately when the following comparisons
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

@@

\begin{theorem}
\label{result}
The Hypothesis \ref{hypothesis} is true.
\end{theorem}

@@

\begin{theorem}
$P = NP$.
\end{theorem}

\begin{proof}
This is a direct consequence of Theorems \ref{argument} and \ref{result}.
\end{proof}

@@

This work is implemented into a Project programmed in Scala \cite{FV19}. In this Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}. We need to install JDK 8 in order to test the Scala Project \cite{OD16}. In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.

\section{Conclusion}

No one has been able to find a polynomial time algorithm for any of more than $300$ important known $\textit{NP--complete}$ problems \cite{GJ79}. A proof of $P = NP$ will have stunning practical consequences, because it leads to efficient methods for solving some of the important problems in $NP$ \cite{CS00}. The consequences, both positive and negative, arise since various $\textit{NP--complete}$ problems are fundamental in many fields \cite{CS00}. This result explicitly concludes supporting the existence of a practical solution for the $\textit{NP--complete}$ problems with a $P = NP$ proof that is actually nonconstructive. All the following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our result:

Cryptography, for example, relies on certain problems being difficult. A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}. These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.

There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems. For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}. Efficient solutions to these problems have enormous implications for logistics \cite{CS00}. Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.

Moreover, Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}. Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}. We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.

But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself. Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated. For instance, Fermat's Last Theorem took over three centuries to prove. A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
